---
title: "HOLIDAYinn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmltools)
library(purrr)
library(knitr)
```

busy bee

```{css html-import-or-backend}
.gallery-wrapper {
display: flex;
overflow-x: hidden;       /*disable scroll function*/
scroll-snap-type: x mandatory;
gap: 16px;
padding: 16px;
background: #f4f4f4;
<<<<<<< HEAD
scroll-behavior: smooth;
=======
-webkit-overflow-scrolling: touch;
>>>>>>> 832f8526fdf2720445a3cfd35b0c422304377341
}

.gallery-card {
flex: 0 0 auto;
width: 540px;
height: 540 px;
scroll-snap-align: start;
position: relative;
border-radius: 8px;
overflow: hidden;
box-shadow: 0 2px 6px rgba(0,0,0, 0.15)
}

.gallery-card img {
width: 100%;
height: 100%;
object-fit: cover;
display: block;
}

.gallery-caption {
position: absolute;
bottom: 0;
left: 0;
right: 0;
padding: 8px 10px;
background: linear-gradient(to top, rgba(0,0,0, 0.7), rgba(0,0,0,0));
color: white;
font-size: 0.9em;
font-family: sans-serif;
}
<<<<<<< HEAD

.gallery-controls {
display: flex;
justify-content: center;
gap: 24px;
padding: 12px 0;
}

.gallery-arrow{
cursor: pointer;
border: none;
background: #333;
color: white;
font-size: 1.2em;
width: 40px;
height: 40px;
border-radius: 50%
}

```                   
 
=======
```

>>>>>>> 832f8526fdf2720445a3cfd35b0c422304377341
yo

```{r build-gallery!}
gallery_data <- data.frame(
  src = c("https://www.reithoffershows.com/wp-content/uploads/2017/08/Merry-Go-Round-1.jpg",
          "https://th.bing.com/th/id/R.1a1492f10f097d83426a46908c117edd?rik=e8Cz6asab%2bePBw&pid=ImgRaw&r=0",
          "https://static.vecteezy.com/system/resources/previews/015/178/788/large_2x/carousel-merry-go-round-in-amusement-park-at-a-night-city-photo.jpg"),
  
  name = c(
    "Researcher 1- Meaty Micheal",
    "Researcher 2- John Pork",
    "Researcher 3 - Tim Cheese"
  ),
  
  caption = c(
    "THE Bringer of Doom",
    "Monarch of Pork",
    "World's Greatest Con-Artist"
  ),
  stringsAsFactors = FALSE
)
   

gallery_cards <-pmap(gallery_data, function(src, caption, name){
  tags$div(
    class = "gallery-card",
    tags$img(src = src, alt = caption),
    tags$div(
      class = "gallery-caption",
      tags$strong(name),
      tags$br(),
      caption
    )
  )
})

gallery <- tags$div(id = "gallery-wrapper", class = "gallery-wrapper", gallery_cards)

controls <- tags$div(
  class = "gallery-controls",
  tags$button(class = "gallery-arrow", onclick = "scrollGallery(-1)", "←"),
  tags$button(class = "gallery-arrow", onclick = "scrollGallery(1)", "→")
)

nav_script <- tags$script(HTML("
  function scrollGallery(direction) {
  var wrapper = document.getElementById('gallery-wrapper');
  var card = wrapper.querySelector('.gallery-card');
  var cardWidth = card.offsetWidth;
  var gap = parseInt(getComputedStyle(wrapper).gap) || 0;
  wrapper.scrollLeft += direction * (cardWidth + gap);
  }
"))

browsable(tagList(gallery, controls, nav_script))
```
